On centrality of even orthogonal $\Kt$

### 2016-04-29 paper.tex
Finished proofreading

In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
%Assume that $I\trianglelefteq R$ such that a short exact sequence
%\renewcommand{\theequation}{$\dagger$}
\setcounter{lm}{1}
\begin{prop}\label{prop:TulPres}
For a splitting ideal $I$ and $n\geq 4$ the group $\St(n,\,R,\,I)$ is isomorphic to the group defined by generators
$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations
\setcounter{equation}{0}
\renewcommand{\theequation}{T\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add2}\\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj2}  \\
&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R) \label{add3}.
\end{align}
Moreover, the group $\St(n, R)$ decomposes into the semidirect product $\St(n,\,R, I)\rtimes \St(n,\,R/I)$.
\end{prop}
Here $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e. matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e. ${}^g X(u,\,v) = X(\phi(s(g))u, \phi(s(g))^*v)$ for $g \in \St(n, R/I)$.

@@

Since columns of elementary matrices are unimodular, one can find $w\in R^t$ such that $w^tv=1$.
It is not hard to check that \setcounter{equation}{6} \setcounter{lm}{7}
\begin{equation} u = (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n, \label{eq:canonical}\end{equation}
therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
Obviously, for $x\in\overline Y(u,\,v)$ and $y\in\overline Y(w,\,v)$ one has $xy\in\overline Y(u+w,\,v)$.

@@

We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
A $B$-module $M$ is called \emph{$r$-divisible} if for every $m\in M$ there exists $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
Clearly, $M$ is $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.

\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is $a$-divisible.
Then for $n\geq 4$ there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
$$\xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
             \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)}$$ \end{tm}

For a vector $u\in R^n$ we denote by $I(u)$ the ideal generated by the entries of $u\in R^n$, i.\,e. $I(u)=\sum\limits_{k=1}^nu_kR$.
To prove \cref{a3map} we follow the approach of Tulenbaev and construct yet another family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily (i.\,e. $X_{u,v}(1) = X(u, v)$).
The key feature of this new family is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation in $a$).
%The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
%One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ .
More formally, we have the following definition.
%Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$. Such generators are defined in~\cite{Tul}.

\begin{df}[Tulenbaev] \label{df:TulX}
For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ such that $v=\sum_{k=1}^Nv_k$ for some $v_1,\ldots,v_N\in B^n$ and that $u^tv_k=0$ and $v_k$ has at least two zero coordinates for all $k$.
Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$. 
\end{df}
Tulenbaev shows that factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other decomposition $v=\sum_{j=1}^Mv'_j$ one has
$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
Thus, the elements $X_{u,v}(a)$ are well-defined. Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.

@@

\begin{lm} \label{xproperties}
For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following facts are true.
\begin{enumerate}
\item $X_{u,vc}(a)=X_{u,v}(ca)$,
\item $X_{uc,v}(ca)=X_{u,vc^2}(a)$,
\item $X_{u,v}(a)X_{u,v'}(a)=X_{u,v+v'}(a)$,
\item $g\,X_{u,wb}(a)g\inv=X_{\phi(g)u,\phi(g)^*wb}(a)$.
\end{enumerate}
\end{lm}

@@

The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition, cf. \eqref{eq:canonical}:
$$(z^tu)w=\sum_{i<j}c_{ij} u_{ij}, \text{ where } u_{ij}=u_je_i-u_ie_j,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
Each $c_{ij}u_{ij}$ is orthogonal to $u$ and because of the assumption $n\geq4$ has at least two zero coordinates.
Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,a c_{ij} u_{ij})$. 
It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*ac_{ij}u_{ij}$ still has two zero coordinates.

Now consider the case $j=h$, $i\neq k$. 
By~\cite[3.12]{vdK} one has $$g\,x(u,\,ac_{ij}u_{ij})g\inv=x(\phi(g)u,\,ac_{ij}\,\phi(g)^*u_{ij}).$$
Set $u' = \phi(g)u$, since
$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = u_je_i - u_ie_j + ru_i e_k =u'_{ij}+r\,u'_{ki},$ 
we obtain from~\cite[3.11]{vdK} that
$$x(\phi(g)u,\,ac_{ij}\,\phi(g)^* u_{ij})=x\left(u',\,c_{ij}a\,u'_{ij}\right)\cdot x\left(u',\,rc_{ij}a\,u'_{ki}\right).$$
Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
 we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}

We will also need the ``transposed'' analogue of Tulenbaev's elements $X_{u,v}(a)$.
\begin{df} \label{df:TulY}
Let $v\in B^n$, $a\in I(v)$, and $u \in D(v)$, i.\,e. $u = \sum\limits_{i=1}^M u_i$ for some $u_k$ having two zero components such that $v^tu_k=0$.
Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
Similarly to \cref{df:TulX} this definition is correct and does not depend neither on the order of factors nor on the choice of decomposition for $u$.
\end{df}

One can repeat van der Kallen's and Tulenbaev's arguments and prove the following transposed version of Lemma~\ref{xproperties}.
We leave the proof of this lemma to the reader.
\begin{lm}
\label{yproperties}
For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in\mathrm I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
\begin{enumerate}
\item $Y_{uc,v}(a)=Y_{u,v}(ca)$,
\item $Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
\item $Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
\item $g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
\end{enumerate}
\end{lm}

Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.

\begin{lm}
\label{x=y}
Let $w$, $u$, $z$, $v$, $x$, $y\in B^n$ be vectors and $a$, $r\in B$ be scalars such that $w^tu=a$, $z^tv=a$, $x^ty=a$.
Suppose that the pairs $(w,\,u)$, $(z,\,v)$ and $(x,\,y)$ are mutually orthogonal. Then $$ X_{u,v}(ra^3)=Y_{u,v}(ra^3).$$
\end{lm}
\begin{proof}
\begin{multline*}
 X_{u,v}(ra^3) = X_{u,y+vra^2}(a)\, X_{u,-y}(a) = X_{t(x,-vra)u,t(x,-vra)^*y}(a)X_{u,-y}(a) = [Y_{x,-v}(ra),\,X_{u,y}(a)] = \\
 = Y_{x,-v}(ra)\, Y_{t(u,ya)x,t(u,ya)^*v}(ra)= Y_{-x,v}(ra)\, Y_{x+ua^2,v}(ra)=Y_{u,v}(ra^3).\qedhere
\end{multline*}
\end{proof}

@@

\begin{proof}[Proof of Theorem~\ref{a3map}]
For $u=Me_1$, $M\in\E(n,\,B_a)$, $v\in I^n$, $u^tv=0$ denote $w=M^*e_1$ (then $wu=1$) and choose $m\in\mathbb N$ such that some $\tilde w$, $\tilde u\in B^n$ localise to $wa^m$ and $ua^m$, $\tilde u^tv=0$ and $\tilde w^t\tilde u=a^{2m}$. Now set $\mathrm T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$. Lemma~\ref{xproperties}\,a) and b) garantees that this definition does not depend on the choice of $m$ and the lifts $\tilde u$ and $\tilde w$. Similarly, set $\mathrm T(S(u,\,v))=Y_{u/a^{3m},\tilde v}(a^{2m})$. These elements satisfy R1--R3 by Lemmas~\ref{xproperties} and~\ref{yproperties}. For $u=Me_1$, $v=M^*e_2$, $M\in\E(n,\,B_a)$ consider $w=M^*e_1$, $z=Me_2$, $x=Me_3$ and $y=M^*e_3$. Then, multiply these element on appropriate power of $a$, take their lifts to $B$ and apply Lemma~\ref{x=y} to get R4. So that, the map $\mathrm T$ is well-defined.

Commutativity of the diagram follows directly from the definitions of elements $X(u,\,v)$, $Y(u,\,v)$ and $X_{u,v}(a)$, $Y_{u,v}(a)$ and the possibility to redistribute the powers of $a$ after localisation.
\end{proof}

>>>>

In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
%Assume that $I\trianglelefteq R$ such that a short exact sequence
%\renewcommand{\theequation}{$\dagger$}
\setcounter{lm}{1}
\begin{prop}\label{prop:TulPres}
For a splitting ideal $I$ and $n\geq 4$ the group $\St(n,\,R,\,I)$ is isomorphic to the group defined by generators
$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations
\setcounter{equation}{0}
\renewcommand{\theequation}{T\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add2}\\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj2}  \\
&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R) \label{add3}.
\end{align}
Moreover, the group $\St(n, R)$ decomposes into the semidirect product $\St(n,\,R, I)\rtimes \St(n,\,R/I)$.
\end{prop}
Here $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e. matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e. ${}^g X(u,\,v) = X(\phi(\sigma(g))u, \phi(\sigma(g))^*v)$ for $g \in \St(n, R/I)$.

@@

Since columns of elementary matrices are unimodular, one can find $w\in R^t$ such that $w^tv=1$.
It is not hard to check that \setcounter{equation}{6} \setcounter{lm}{7}
\begin{equation} (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n, \label{eq:canonical}\end{equation}
therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
Obviously, for $x\in\overline Y(u,\,v)$ and $y\in\overline Y(w,\,v)$ one has $xy\in\overline Y(u+w,\,v)$.

@@

We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
Clearly, $M$ is uniquely $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.

\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is uniquely $a$-divisible.
Then for $n\geq 4$ there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
\begin{equation} \xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
                            \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)} \label{eq:a3diag} \end{equation} \end{tm}

For a vector $u\in R^n$ we denote by $I(u)$ the ideal generated by the entries of $u\in R^n$, i.\,e. $I(u)=\sum\limits_{k=1}^nu_kR$.
To prove \cref{a3map} we follow the approach of Tulenbaev and construct yet another family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily (i.\,e. $X_{u,v}(1) = X(u, v)$).
The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation in $a$).
%The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
%One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ .
%More formally, we have the following definition.
%Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$. Such generators are defined in~\cite{Tul}.

\setcounter{df}{1}
\begin{df} \label{df:TulX}
For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ decomposing into a sum $v=\sum_{k=1}^Nv_k$ where $v_1,\ldots,v_N\in B^n$ are such that $u^tv_k=0$ and each $v_k$ has at least two zero coordinates.
Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$.
\end{df}
Tulenbaev shows that factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other decomposition $v=\sum_{j=1}^Mv'_j$ one has
$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
Thus, the elements $X_{u,v}(a)$ are well-defined. Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.

\begin{rk} \label{rk:ID}
From the canonical decomposition~\eqref{eq:canonical} it follows that $bv\in D(u)$ for any $b\in I(u)$ and $v$ such that $v^tu=0$.
In particular, if $I$ is uniquely $a$-divisible and $a^k\in I(u)$, then every $v\in I^n$ satisfying $v^tu=0$ is contained in $D(u)$.
\end{rk}

@@

\begin{lm} \label{xproperties}
For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following are true:
\begin{enumerate}
\item $X_{u,vc}(a)=X_{u,v}(ca)$,
\item $X_{uc,v}(ca)=X_{u,vc^2}(a)$,
\item $X_{u,v}(a)X_{u,v'}(a)=X_{u,v+v'}(a)$,
\item $g\,X_{u,wb}(a)g\inv=X_{\phi(g)u,\phi(g)^*wb}(a)$.
\end{enumerate}
\end{lm}

@@

The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. We will give a detailed proof of this fact.
Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition \eqref{eq:canonical}:
$$(z^tu)w=\sum_{i<j}c_{ij} u_{ij}, \text{ where } u_{ij}=u_je_i-u_ie_j,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
Each $c_{ij}u_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,a c_{ij} u_{ij})$. 
It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*ac_{ij}u_{ij}$ still has two zero coordinates.

Now consider the case $j=h$, $i\neq k$. 
By~\cite[3.12]{vdK} one has $$g\,x(u,\,ac_{ij}u_{ij})g\inv=x(\phi(g)u,\,ac_{ij}\,\phi(g)^*u_{ij}).$$
Set $u' = \phi(g)u$, since
$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = u_je_i - u_ie_j + ru_i e_k =u'_{ij}+r\,u'_{ki},$ 
we obtain from~\cite[3.11]{vdK} that
$$x(\phi(g)u,\,ac_{ij}\,\phi(g)^* u_{ij})=x\left(u',\,c_{ij}a\,u'_{ij}\right)\cdot x\left(u',\,rc_{ij}a\,u'_{ki}\right).$$
Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g^{-1}$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
 we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}

We will also need the ``transposed'' analogue of Tulenbaev's elements $X_{u,v}(a)$.
\begin{df} \label{df:TulY}
Let $v\in B^n$, $a\in I(v)$, and $u \in D(v)$, i.\,e. $u = \sum\limits_{i=1}^M u_i$ for some $u_k$ having two zero components such that $v^tu_k=0$.
Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
Similarly to \cref{df:TulX} this definition does not depend neither on the order of factors nor on the choice of decomposition for $u$.
\end{df}

One can repeat van der Kallen's and Tulenbaev's arguments and prove the following transposed version of Lemma~\ref{xproperties}.
We leave the proof of this lemma to the reader.
\begin{lm}
\label{yproperties}
For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
\begin{enumerate}
\item $Y_{uc,v}(a)=Y_{u,v}(ca)$,
\item $Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
\item $Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
\item $g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
\end{enumerate}
\end{lm}

Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
\begin{lm}\label{x=y}
Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b,r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$ and $b\in I(u)\cap I(v)$.
Then one has $X_{u,b^4rv}(b)=Y_{b^4ru,v}(b).$
\end{lm}
\begin{proof}
Compute $g=[Y_{-arx,v}(b),\,X_{u,ay}(b)]$ in two different ways using Lemmas~\ref{xproperties}~and~\ref{yproperties}:
$$ g = X_{t(b^2rx,-v)u,\,t(b^2rx,-v)^*yb}(b)X_{u,-yb}(b) = X_{u,\,by+b^4rv}(b)\, X_{u,-by}(b) = X_{u,b^4rv}(b),$$
$$ g = Y_{-brx,v}(b) Y_{t(u,b^2y)arx,\,t(u,b^2y)^*v}(b)= Y_{-brx,v}(b)\, Y_{brx+b^4ru,\,v}(b)=Y_{b^4ru,v}(b).\qedhere$$
\end{proof}

@@

\begin{proof}[Proof of Theorem~\ref{a3map}]
Consider $u=Me_1$, $M\in\E(n,\,B_a)$ and $v\in I^n$ such that $u^tv=0$.
Set $w=M^*e_1$. Since $w^tu=1$ there exist vectors $\tilde w$, $\tilde u\in B^n$ and a natural number $m$ such that 
$$ \lambda_a(\tilde{w})=wa^m,\ \lambda_a(\tilde{u})=ua^m\text{ and moreover }\tilde u^tv=0\text{ and }\tilde w^t\tilde u=a^{2m}.$$
It is clear that $a^{2m}\in I(\tilde u)$, moreover by~\cref{rk:ID} we have $v/a^{3m} \in D(\tilde u)$, therefore we are allowed to set $T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$.

The first two assertions of \cref{xproperties} guarantee that this definition does not depend on the choice of $m$ and the liftings $\tilde u$ and $\tilde w$.
Similarly, we can define $T(S(u,\,v))=Y_{u/a^{3m},\tilde v}(a^{2m})$.
In view of Lemmas~\ref{xproperties}~and~\ref{yproperties} the map $T$ preserves relations \eqref{add4}--\eqref{conj3}.

It remains to check for $u = Me_1$, $v=M^*e_2$ and $c\in I$ that 
\begin{equation}T(F(u, bv)) = X_{\tilde u,c/a^{4m}\,\tilde v}(a^{2m}) = Y_{c/a^{4m}\, \tilde u,\tilde v}(a^{2m}) = T(S(ub, v)). \label{eq:last}\end{equation}
Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)=a^m u$, $\lambda_a(\tilde v)=a^m v$ and $\tilde u^t \tilde v = 0$.
We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
$$\lambda_a(\tilde{x})=a^mMe_3,\ \lambda_a(\tilde{y})=a^mM^*e_3\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.
Thus, the map $T$ is well-defined.

Commutativity of the diagram~\eqref{eq:a3diag} follows directly from the definitions of elements $X(u,\,v)$, $Y(u,\,v)$ and $X_{u,v}(a)$, $Y_{u,v}(a)$. \end{proof}
